---
title: "Data Pre-processing"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '01_01_data_preprocess.html'))})
---

## Data Preparation

### Dataset
Following the 7.8 Mw Gorkha Earthquake in Nepal on April 25, 2015, the Kathmandu Living Labs in collaboration with the National Planning Commission (the Government of Nepal), carried out the largest household survey ever done in Nepal using mobile technology. Although the primary objective of this survey was to assess damages inflicted by the quake and identify beneficiaries eligible for government’s housing reconstruction grants, the data contain many other kinds of valuable socio-economic information, including the types of fuel used by households for cooking and lighting from 11 of the most earthquake-affected districts of Nepal, excluding the Kathmandu valley. 

The data for all 11 districts were downloaded from the **2015 Nepal Earthquake: Open Data Portal** (<http://eq2015.npc.gov.np/>). For this study, we use the following two data files:

1. **csv_household_demographics.csv**; this file contains information on household size, ethnicity, household income, and gender, education and age of household head, and
2. **csv_household_resources.csv**; this file contains data on the type of fuel used by households for cooking and lighting, source of drinking water, and the ownership of electronic appliances and motor vehicles.


### Data Preparation
We restrict our analysis to four key socio-economic and demographic information of the households (ethnicity, income, education, and location) and their post-earthquake sources of cooking fuel.

**Ethnicity**: The dataset includes the types of cooking fuel used by 96 different social groups found in the area. Since the relative population sizes of many of these groups are small, we regroup them together to form a larger group with comparable population size; we also merge some of them with the larger major groups to which they are closer culturally or linguistically. With this regrouping, we obtain 10 major ethnic groups: 

* Brahman, 
* Chepang-Thami, 
* Chhettri, 
* Dalit, 
* Gurung-Magar, 
* Madheshi, 
* Newar, 
* Rai-Limbu, 
* Tamang, and 
* Muslim-Others.

**Education Level**: The education level of the household heads range from illiterate to Doctoral degree. We regroup the education attainment into 5 levels: 

* Illiterate; 
* Non-formal and Others; 
* grade 1-7 as Primary; 
* grade 8-12 as Secondary; and 
* Bachelors, Masters, and PhDs as University level education. 

**Geo-climatic Region**: Similarly, the data provide information on municipality (and ward-level) location which allows us to divide the entire earthquake-affected 11 contiguous districts into two geo-climatic regions: 

* Himalayan and 
* Hilly. 

**Income Group**: As for income levels (Rs. 110 = USD 1, approx.), we follow the original dataset's categorization that breaks the monthly income of the households into 5 levels:

* Rs. 10,000 or less; 
* Rs. 10,000 to 20,000; 
* Rs. 20,000 to 30,000; 
* Rs. 30,000 to 50,000; and
* more than Rs. 50,000. 
<br/><br/>


#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
library("stringr")
library("dplyr")
library("reshape2")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "data/data_household")
dir.annot <- file.path(dir.wrk, "data/data_annotations")
dir.output <- file.path(dir.wrk, "data/data_processed")
```


#### Define Files
```{r tidy=TRUE}
file.household_demo <- file.path(dir.data, "csv_household_demographics.csv.gz")
file.household_res <- file.path(dir.data, "csv_household_resources.csv.gz")
file.map_loc <- file.path(dir.data, "ward_vdcmun_district_name_mapping.csv.gz")
file.eth_grp <- file.path(dir.annot, "group_ethnicity.tsv")
file.edu_grp <- file.path(dir.annot, "group_education.tsv")
file.geo_grp <- file.path(dir.annot, "group_georegion.tsv")
```

#### Load Location Lookup Tables
```{r tidy=TRUE}
dat.map <- read.csv(file.map_loc, header=TRUE, stringsAsFactors=FALSE)
dat.map <- dat.map[!duplicated(dat.map),]
dat.map$ward_num <- unlist(lapply(str_split(dat.map$ward_id, ""), 
                                  function(x) as.numeric(paste(x[length(x)-1], x[length(x)], sep="") )))

lookup_dist <- subset(dat.map, select=c("district_id","district_name"))
lookup_dist <- lookup_dist[!duplicated(lookup_dist),]

head(lookup_dist)
```

#### Load Grouping Data
```{r tidy=TRUE}
dat.eth <- read.delim(file.eth_grp, header=TRUE, stringsAsFactors=FALSE)
dat.edu <- read.delim(file.edu_grp, header=TRUE, stringsAsFactors=FALSE)
dat.geo <- read.delim(file.geo_grp, header=TRUE, stringsAsFactors=FALSE)

head(dat.geo)
```

#### Load Household Data
```{r tidy=TRUE}
dat.household_demo <- read.csv(file.household_demo, header=TRUE, stringsAsFactors=FALSE)
dat.household_res <- read.csv(file.household_res, header=TRUE, stringsAsFactors=FALSE)

### MERGE DATA ---
dat.household <- Reduce(function(x, y) merge(x, y, all=TRUE), 
                        list(dat.household_demo, dat.household_res, by="household_id"))

### TRIM DATA ---
items <- c("household_id","district_id","vdcmun_id",
           "source_cooking_fuel_post_eq","caste_household",
           "income_level_household","education_level_household_head")
dat.household <- subset(dat.household, select=items)
```

#### Add District Names
```{r tidy=TRUE}
dat.household$District <- NA
for(i in 1:nrow(lookup_dist)){
  index <- which(dat.household$district_id == lookup_dist$district_id[i])  
  dat.household$District[index] <- lookup_dist$district_name[i]
}
```

#### Add GeoRegion
```{r tidy=TRUE}
dat.household$GeoRegion <- NA
for(i in 1:nrow(dat.geo)){
  index <- which(dat.household$vdcmun_id == dat.geo$vdcmun_id[i])  
  dat.household$GeoRegion[index] <- dat.geo$Region[i]
}
```

#### Categorize Income
```{r tidy=TRUE}
dat.household$IncomeGroup <- NA
dat.household$IncomeGroup[which(dat.household$income_level_household == "Rs. 10 thousand")] <- "0-10000"
dat.household$IncomeGroup[which(dat.household$income_level_household == "Rs. 10-20 thousand")] <- "10000-20000"                                              
dat.household$IncomeGroup[which(dat.household$income_level_household == "Rs. 20-30 thousand")] <- "20000-30000"
dat.household$IncomeGroup[which(dat.household$income_level_household == "Rs. 30-50 thousand")] <- "30000-50000"
dat.household$IncomeGroup[which(dat.household$income_level_household == "Rs. 50 thousand or more")] <- "50000-ABOVE"
```

#### Categorize Ethnicity
```{r tidy=TRUE}
dat.household$Ethnicity <- NA
for(i in 1:nrow(dat.eth)){
  index <- which(dat.household$caste_household == dat.eth$Caste[i])  
  dat.household$Ethnicity[index] <- dat.eth$Ethnicity[i]
}
```

#### Categorize Educational Level
```{r tidy=TRUE}
dat.household$EducationLevel <- NA
for(i in 1:nrow(dat.edu)){
  index <- which(dat.household$education_level_household_head == dat.edu$EducationLevel[i])  
  dat.household$EducationLevel[index] <- dat.edu$EducationGroup[i]
}
```

#### Trim Data
```{r tidy=TRUE}
dat.household <- dat.household[-which(is.na(dat.household$Ethnicity)),]

### TRIM DATA ---
items <- c("household_id","District","GeoRegion",
           "Ethnicity","IncomeGroup","EducationLevel",
           "source_cooking_fuel_post_eq")
dat.household <- subset(dat.household, select=items)
dat.household <- dat.household %>% dplyr::mutate_all(as.character)

head(dat.household)

# WRITE OUTPUT ---
file.output <- file.path(dir.output, "household_level_data_categorical.tsv")
write.table(dat.household, file.output, sep="\t", row.names=FALSE, col.names=TRUE, quote=FALSE)
```

#### Prepare Frequency Table
```{r tidy=TRUE}
df <- dat.household %>% 
        dplyr::count(Ethnicity, EducationLevel, GeoRegion, IncomeGroup, source_cooking_fuel_post_eq, sort=FALSE, name="Freq")

head(df)
```


#### Impute Missing Values 
```{r tidy=TRUE}
dkey <- apply(df, 1, function(x) paste(x[1:5], collapse=":"))

var1 <- setdiff(unique(df$Ethnicity), NA)
var2 <- setdiff(unique(df$EducationLevel), NA)
var3 <- setdiff(unique(df$GeoRegion), NA)
var4 <- setdiff(unique(df$IncomeGroup), NA)
var5 <- setdiff(unique(df$source_cooking_fuel_post_eq), NA)
dcom <- expand.grid(var1,var2,var3,var4,var5)
dcom$key <- apply(dcom, 1, function(x) paste(x[1:5], collapse=":"))

var.missed <- setdiff(dcom$key, dkey)
dcom <- subset(dcom, dcom$key %in% var.missed)
dcom <- dcom[,-6]
dcom$Freq <- 0
colnames(dcom) <- colnames(df)

# MERGE DATA WITH RESCUED COMBINATION ---
df <- rbind(df, dcom)
df <- df[order(df$Ethnicity, df$EducationLevel, df$GeoRegion, 
               df$IncomeGroup, df$source_cooking_fuel_post_eq),]

dim(df)
tail(df)

# WRITE OUTPUT ---
file.output <- file.path(dir.output, "household_level_data_frequency.tsv")
write.table(df, file.output, sep="\t", row.names=FALSE, col.names=TRUE, quote=FALSE)
```

#### Prepare Frequency Table by FuelType Per Column
```{r tidy=TRUE}
df <- subset(df, !(is.na(df$Ethnicity)))
df <- subset(df, !(is.na(df$source_cooking_fuel_post_eq)))
dm <- reshape2::dcast(data=df, 
                  formula=Ethnicity+EducationLevel+GeoRegion+IncomeGroup~source_cooking_fuel_post_eq, 
                  fun.aggregate=sum, value.var="Freq")
colnames(dm) <- c("Ethnicity","EducationLevel","GeoRegion","IncomeGroup",
                  "Electricity","GobarGas","Kerosene","LPGas","Others","Wood")

head(dm)

# WRITE OUTPUT ---
file.output <- file.path(dir.output, "household_level_data_frequency_table.tsv")
write.table(dm, file.output, sep="\t", row.names=FALSE, col.names=TRUE, quote=FALSE)
```

