---
title: "Generate Choropleth Maps"

output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '02_02_maps_plot.html'))})
---

### Data Preparation
We obtained the geographical coordinates of Nepal's administrative units (District Level: 77 Districts) in GeoJSON format from the **Open Knowledge Nepal** data portal (http://localboundries.oknp.org/). <br/><br/>

#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
library("stringr")
library("dplyr")
library("reshape2")
library("geojsonio")
library("broom")
library("ggplot2")
library("ggthemes")
library("RColorBrewer")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "data/data_household")
dir.annot <- file.path(dir.wrk, "data/data_annotations")
dir.output <- file.path(dir.wrk, "data/data_processed")
dir.maps <- file.path(dir.wrk, "data/data_maps")
```

#### Define Files
```{r tidy=TRUE}
file.geo <- file.path(dir.maps, "nepal_district.geojson")
file.dat1 <- file.path(dir.output, "maps_tbl_district_total_household.tsv")
file.dat2 <- file.path(dir.output, "maps_tbl_district_fueltype_ratio.tsv")
file.dat3 <- file.path(dir.output, "maps_tbl_district_ethnicity_ratio.tsv")
```

#### Load Household Population by District
```{r tidy=TRUE}
dat1 <- read.delim(file.dat1, header=TRUE, stringsAsFactors=FALSE)

head(dat1)
```

#### Load Maps
```{r echo=TRUE, message=FALSE, warning=FALSE}
geo <- geojsonio::geojson_read(file.geo, parse=TRUE, what="sp")
geo77 <- broom::tidy(geo, region="DISTRICT")
geo11 <- subset(geo77, geo77$id %in% dat1$id)

head(geo11)
```

#### Plot Choropleth Maps: Nepal with all Districts
```{r fig.align = "center"}
# PREPARE DATA ---
d <- geo77
d$Status <- 0
d$Status[which(d$id %in% dat1$id)] <- 1
d$Status <- as.factor(d$Status)

# DEFINE COLORS ---
cpalette.grp <- c("#FFFFFF","#BDBDBD")

# PLOT
map77 <- ggplot(data=d, aes(x=long, y=lat, group=group)) +
          geom_path() +
          geom_polygon(aes(fill=Status), color="#000000") +
          scale_fill_manual(values=cpalette.grp) +
          coord_equal() +
          theme_map() +
          theme(
            plot.title = element_text(size = 10, color="#000000", hjust=0.5),
            #aspect.ratio = 1,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            axis.ticks = element_blank(),	
            strip.text = element_text(size = 10, color="#000000", hjust=0.5),
            strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
            panel.background = element_rect(fill="#FFFFFF", color=NA),
            legend.text = element_text(size = 10, color="#000000"),
            legend.title = element_blank(),
            legend.key.size = unit(0.5, "cm"),
            legend.position = "none") +
          guides(fill=guide_legend(title="No. of Households"))

map77
```

#### Load Household Population by Earthquake-affected Districts
```{r tidy=TRUE}
dat1 <- read.delim(file.dat1, header=TRUE, stringsAsFactors=FALSE)

# CONVERT TO DISCRETE DATA ---
dm <-  mutate(dat1, Group=cut(Freq, seq(10000, 100000, 10000), include.lowest = TRUE)) %>% 
              group_by(Group) 
group_ratio <- levels(dm$Group)

# MERGE DATA ---
df <- merge(geo11, dm, by="id")
head(df)
```


#### Plot Choropleth Maps: Total No. of Households
```{r fig.height = 7, fig.width = 7, fig.align = "center"}
map1 <- ggplot(data=df, aes(x=long, y=lat, group=group, fill=Group)) +
          geom_path() +
          geom_polygon(aes(fill=Group), color="#000000") +
          scale_fill_brewer(palette = "Blues") +
          coord_equal() +
          theme_map() +
          theme(
            plot.title = element_text(size = 10, color="#000000", hjust=0.5),
            aspect.ratio = 1,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            axis.ticks = element_blank(),	
            strip.text = element_text(size = 10, color="#000000", hjust=0.5),
            strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
            panel.background = element_rect(fill="#FFFFFF", color=NA),
            legend.text = element_text(size = 10, color="#000000"),
            legend.title = element_text(size = 10, color="#000000"),
            legend.key.size = unit(0.5, "cm"),
            legend.position = "right") +
          guides(fill=guide_legend(title="No. of Households", ncol=1))

map1
```

#### Load Household FuelType Usage Proportions by Earthquake affected Districts
```{r tidy=TRUE}
dat2 <- read.delim(file.dat2, header=TRUE, stringsAsFactors=FALSE)

head(dat2)

# CONVERT TO DISCRETE DATA ---
dm <- reshape2::melt(dat2, id.vars="id", variable.name="FuelType", value.name="Ratio")
dm <-  mutate(dm, RatioGroup=cut(Ratio, seq(0,0.25,0.05), include.lowest = TRUE)) %>% 
              group_by(RatioGroup)

group_ratio <- levels(dm$RatioGroup)
type_fuel <- c("Wood","LP.Gas","Gobar.Gas","Kerosene","Electricity", "Others")

# MERGE DATA ---
df <- merge(geo11, dm, by="id")

# FACTORIZE DATA ---
df$FuelType <- factor(df$FuelType, levels=type_fuel)
df$RatioGroup <- factor(df$RatioGroup, levels=group_ratio)

head(df)
```

#### Plot Choropleth Maps: Proportion of Households using six FuelTypes
```{r fig.height = 7, fig.width = 7, fig.align = "center"}
map2 <- ggplot(data=df, aes(x=long, y=lat, group=group, fill=RatioGroup)) +
          geom_path() +
          geom_polygon(aes(fill=RatioGroup), color="#000000") +
          scale_fill_brewer(palette = "Blues") +
          facet_wrap(~FuelType, ncol=3, drop=FALSE,  strip.position="top") +
          coord_equal() +
          theme_map() +
          theme(
               plot.title = element_text(size = 10, color="#000000", hjust=0.5),
               aspect.ratio = 1,
               panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               axis.ticks = element_blank(),	
               strip.text = element_text(size = 10, color="#000000", hjust=0.5),
               strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
               panel.background = element_rect(fill="#FFFFFF", color=NA),
               legend.text = element_text(size = 10, color="#000000"),
               legend.title = element_text(size = 10, color="#000000"),
               legend.key.size = unit(0.5, "cm"),
               legend.position = "right") +
          guides(fill=guide_legend(title="Proportion of Households", ncol=1))

map2
```


#### Load Household Population by Ethnicity and District
```{r tidy=TRUE}
dat3 <- read.delim(file.dat3, header=TRUE, stringsAsFactors=FALSE)

head(dat3)

# CONVERT TO DISCRETE DATA ---
dm <- reshape2::melt(dat3, id.vars="id", variable.name="Ethnicity", value.name="Ratio")
dm <-  mutate(dm, RatioGroup=cut(Ratio, seq(0,0.4,0.05), include.lowest = TRUE)) %>% 
              group_by(RatioGroup)

group_ratio <- levels(dm$RatioGroup)
type_ethnicity <- c("Newar","Brahman","Madhesi","Chettri","Muslim.Others",
                         "Gurung.Magar","Dalit","Rai.Limbu","Tamang","Chepang.Thami")

# MERGE DATA ---
df <- merge(geo11, dm, by="id")

# FACTORIZE DATA ---
df$Ethnicity <- factor(df$Ethnicity, levels=type_ethnicity)
df$RatioGroup <- factor(df$RatioGroup, levels=group_ratio)

head(df)
```


#### Plot Choropleth Maps: Proportion of Households by Ethnicity
```{r fig.height = 7, fig.width = 7, fig.align = "center"}
map3 <- ggplot(data=df, aes(x=long, y=lat, group=group, fill=RatioGroup)) +
          geom_path() +
          geom_polygon(aes(fill=RatioGroup), color="#000000") +
          scale_fill_brewer(palette = "Blues") +
          facet_wrap(~Ethnicity, ncol=4, drop=FALSE,  strip.position="top") +
          coord_equal() +
          theme_map() +
          theme(
               plot.title = element_text(size = 10, color="#000000", hjust=0.5),
               aspect.ratio = 1,
               panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               axis.ticks = element_blank(),	
               strip.text = element_text(size = 10, color="#000000", hjust=0.5),
               strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
               panel.background = element_rect(fill="#FFFFFF", color=NA),
               legend.text = element_text(size = 10, color="#000000"),
               legend.title = element_text(size = 10, color="#000000"),
               legend.key.size = unit(0.5, "cm"),
               legend.position = "right") +
          guides(fill=guide_legend(title="Proportion of Households", ncol=1))

map3
```
