---
title: "Explore Baseline Data"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '03_01_baseline_data.html'))})
---

#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
library("stringr")
library("dplyr")
library("reshape2")
library("ggplot2")
library("gplots")
library("RColorBrewer")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "data/data_household")
dir.annot <- file.path(dir.wrk, "data/data_annotations")
dir.output <- file.path(dir.wrk, "data/data_processed")
```

#### Define Files
```{r tidy=TRUE}
file.dat <- file.path(dir.output, "household_level_data_categorical.tsv")
```

#### Define Categories
```{r}
type_ethnicity <- c("Newar","Brahman","Madhesi","Chettri","Muslim−Others",
                    "Gurung−Magar","Dalit","Rai−Limbu","Tamang","Chepang−Thami")
type_fuel <- c("Wood","LP Gas","Gobar Gas","Kerosene","Electricity","Others")
type_geo <- c("Himalayan","Hilly")

cpalette.eth <- c("#e31a1c","#a6cee3","#1f78b4","#b2df8a","#33a02c",
                  "#fb9a99","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a")
cpalette.inc <- c("#fdd49e","#fdbb84","#fc8d59","#e34a33","#b30000")
cpalette.edu <- c("#bfd3e6","#9ebcda","#8c96c6","#8856a7","#810f7c")
```

#### Load Data
```{r tidy=TRUE}
dat <- read.delim(file.dat, header=TRUE, stringsAsFactors=FALSE)
dat <- dat %>% dplyr::mutate_all(as.character)

# FACTORIZE DATA ---
dat$source_cooking_fuel_post_eq <- factor(dat$source_cooking_fuel_post_eq, levels=type_fuel)
dat$Ethnicity <- factor(dat$Ethnicity, levels=type_ethnicity)

head(dat)
```

#### Get Proportion of Households using each FuelType
```{r}
df <- dat %>% 
          dplyr::count(source_cooking_fuel_post_eq, sort=FALSE, name="Freq") %>%
          mutate(Proportion= Freq/sum(Freq))
df$Group <- "Total Household"
df$source_cooking_fuel_post_eq <- factor(df$source_cooking_fuel_post_eq, levels=type_fuel)

head(df)
```


#### Plot Proportion of Households by FuelType use
```{r fig.height = 4, fig.width = 3, fig.align = "center"}
# COLOR PALETTE ---
jColFun <- colorRampPalette(brewer.pal(n = 9, "Set1"))

# PLOT ---
p1 <- ggplot(df, aes(x=Group, y=Proportion)) + 
        geom_bar(aes(fill=source_cooking_fuel_post_eq), stat="identity", color=NA, width=0.8, size=0.5) + 
        scale_fill_manual(values=jColFun(6)) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Proportion of Household") +
      xlab("") + 
      ggtitle("") 

p1
```


#### Get Household Proportion by Ethnicity and Income for each FuelType
```{r}
dm <- dat %>% 
          dplyr::count(Ethnicity, IncomeGroup, source_cooking_fuel_post_eq, sort=FALSE, name="Freq") %>%
          group_by(Ethnicity, IncomeGroup) %>%
          mutate(Proportion=Freq/sum(Freq))

dm$source_cooking_fuel_post_eq <- factor(dm$source_cooking_fuel_post_eq, levels=type_fuel)
dm$Ethnicity <- factor(dm$Ethnicity, levels=type_ethnicity)

head(dm)
```


#### Plot Household Proportion by Ethnicity and Income for each FuelType
```{r fig.height = 4, fig.width = 8, fig.align = "center"}
# COLOR PALETTE ---
jColFun <- colorRampPalette(brewer.pal(n = 9, "Set1"))

# PLOT ---
p2 <- ggplot(dm, aes(x=IncomeGroup, y=Proportion)) + 
        geom_bar(aes(fill=source_cooking_fuel_post_eq), stat="identity", color="#000000", width=0.8, size=0.5) + 
        scale_fill_manual(values=jColFun(6)) +
        facet_wrap(~Ethnicity, ncol=5, scales="fixed", drop=FALSE, strip.position="top") +
        theme(
          axis.text.x = element_text(size = 10, color="#000000", angle=90, hjust=1, vjust=0.5),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Proportion of Household") +
      xlab("Income Group") + 
      ggtitle("") 

p2
```

#### Get Household Proportion by Ethnicity and Education Level for each FuelType
```{r}
dm <- dat %>% 
          dplyr::count(Ethnicity, EducationLevel, source_cooking_fuel_post_eq, sort=FALSE, name="Freq") %>%
          group_by(Ethnicity, EducationLevel) %>%
          mutate(Proportion=Freq/sum(Freq))

dm$source_cooking_fuel_post_eq <- factor(dm$source_cooking_fuel_post_eq, levels=type_fuel)
dm$EducationLevel <- as.factor(dm$EducationLevel)

head(dm)
```

#### Plot Household Proportion by Ethnicity and Education Level for each FuelType
```{r fig.height = 4, fig.width = 8, fig.align = "center"}
# COLOR PALETTE ---
jColFun <- colorRampPalette(brewer.pal(n = 9, "Set1"))

# PLOT ---
p3 <- ggplot(dm, aes(x=EducationLevel, y=Proportion)) + 
        geom_bar(aes(fill=source_cooking_fuel_post_eq), stat="identity", color="#000000", width=0.8, size=0.5) + 
        scale_fill_manual(values=jColFun(6)) +
        facet_wrap(~Ethnicity, ncol=5, scales="fixed", drop=FALSE, strip.position="top") +
        theme(
          axis.text.x = element_text(size = 10, color="#000000", angle=90, hjust=1, vjust=0.5),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Proportion of Household") +
      xlab("Education Level") + 
      ggtitle("") 

p3
```

#### Get Household Proportion by Ethnicity and Geo-climatic Region for each FuelType 
```{r}
dm <- dat %>% 
          dplyr::count(Ethnicity, GeoRegion, source_cooking_fuel_post_eq, sort=FALSE, name="Freq") %>%
          group_by(Ethnicity, GeoRegion) %>%
          mutate(Proportion=Freq/sum(Freq))

dm$source_cooking_fuel_post_eq <- factor(dm$source_cooking_fuel_post_eq, levels=type_fuel)
dm$GeoRegion <- factor(dm$GeoRegion, levels=type_geo)

head(dm)
```


#### Plot Household Proportion by Ethnicity and Geo-climatic Region for each FuelType 
```{r fig.height = 4, fig.width = 8, fig.align = "center"}
# COLOR PALETTE ---
jColFun <- colorRampPalette(brewer.pal(n = 9, "Set1"))

# PLOT ---
p4 <- ggplot(dm, aes(x=GeoRegion, y=Proportion)) + 
        geom_bar(aes(fill=source_cooking_fuel_post_eq), stat="identity", color="#000000", width=0.8, size=0.5) + 
        scale_fill_manual(values=jColFun(6)) +
        facet_wrap(~Ethnicity, ncol=5, scales="fixed", drop=FALSE, strip.position="top") +
        theme(
          axis.text.x = element_text(size = 10, color="#000000", angle=90, hjust=1, vjust=0.5),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Proportion of Household") +
      xlab("Geo-climatic Region") + 
      ggtitle("") 

p4
```

#### Household Population Distribution by Ethnicity
```{r}
dm <- dat %>% 
        dplyr::count(Ethnicity, sort=TRUE, name="Freq") %>%
        mutate(Percentage= (Freq/sum(Freq)) * 100)
dm$Country <- "Nepal"

# Factorize data
dm$Ethnicity <- factor(dm$Ethnicity, levels=type_ethnicity)

head(dm)
```

#### Plot Household Proportion by Ethnicity
```{r fig.height = 4, fig.width = 3, fig.align = "center"}
# PLOT ---
p5 <- ggplot(dm, aes(x=Country, y=Percentage)) + 
        geom_bar(aes(fill=Ethnicity), stat="identity", color=NA, width=0.8, size=0.5) + 
        scale_fill_manual(values=cpalette.eth) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Percentage of Household") +
      xlab("Ethnicity") + 
      ggtitle("") 

p5
```



#### Household Population Distribution by IncomeGroup
```{r}
dm <- dat %>% 
        dplyr::count(IncomeGroup, sort=TRUE, name="Freq") %>%
        mutate(Percentage= (Freq/sum(Freq)) * 100)
dm$Country <- "Nepal"

# Factorize data
dm$IncomeGroup <- as.factor(dm$IncomeGroup)

head(dm)
```

#### Plot Household Proportion by IncomeGroup
```{r fig.height = 4, fig.width = 3, fig.align = "center"}
# PLOT ---
p6 <- ggplot(dm, aes(x=Country, y=Percentage)) + 
        geom_bar(aes(fill=IncomeGroup), stat="identity", color=NA, width=0.8, size=0.5) + 
        scale_fill_manual(values=cpalette.inc) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Percentage of Household") +
      xlab("IncomeGroup") + 
      ggtitle("") 

p6
```


#### Household Population Distribution by EducationLevel
```{r}
dm <- dat %>% 
        dplyr::count(EducationLevel, sort=TRUE, name="Freq") %>%
        mutate(Percentage= (Freq/sum(Freq)) * 100)
dm$Country <- "Nepal"

# Factorize data
dm$IncomeGroup <- as.factor(dm$EducationLevel)

head(dm)
```

#### Plot Household Proportion by EducationLevel
```{r fig.height = 4, fig.width = 3, fig.align = "center"}
# PLOT ---
p7 <- ggplot(dm, aes(x=Country, y=Percentage)) + 
        geom_bar(aes(fill=EducationLevel), stat="identity", color=NA, width=0.8, size=0.5) + 
        scale_fill_manual(values=cpalette.edu) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "right") +
      ylab("Percentage of Household") +
      xlab("EducationLevel") + 
      ggtitle("") 

p7
```


#### Get Abundance (Number of Households) by Ethnicity and FuelType
```{r}
df <- dat %>% dplyr::count(Ethnicity, source_cooking_fuel_post_eq, sort=FALSE, name="Freq")
dm <- reshape2::dcast(data=df, formula=Ethnicity ~ source_cooking_fuel_post_eq, fun.aggregate=sum, value.var="Freq")
head(dm)
```

#### Total Transformation (To Get Relative Abundance Values)
```{r}
# TOTAL TRANSFORMATION ---
dmt <- vegan::decostand(dm[,2:7], "total")
rownames(dmt) <- dm$Ethnicity
dmt <- dmt[match(rev(type_ethnicity), rownames(dmt)),]
                               
dmt
```

#### Heatmap for Relative Abundance by Ethnicity and FuelType
```{r fig.align = "center"}
jColFun <- colorRampPalette(brewer.pal(n = 9, "Reds"))

heatmap.2(as.matrix(dmt), col = jColFun(256), margin=c(8,15),
          Colv=TRUE, Rowv = FALSE, cexRow=1, cexCol=1,
          dendrogram ="none", trace="none", main="",
          hclustfun = function(x) hclust(x, method = "ward.D2"), 
          distfun = function(x) dist(x, method = "euclidean"),
          colsep=c(1:50), rowsep=c(1:50),
          sepcolor="#BDBDBD", sepwidth=c(0.0005,0.0005), 
          key="TRUE", keysize=1, density.info="none", 
          key.title = NA, key.xlab = NA, key.ylab = NA,
          key.par=list(mgp=c(1.5, 0.5, 0), mar=c(2.5, 2.5, 1, 0)))
```

#### Get Distance Matrix of Ethnicity based on FuelType Usage
```{r}
# LOG TRANSFORMATION ---
dml <- vegan::decostand(dm[,2:7], "log")
dist_dml <- vegan::vegdist(x=as.matrix(dml), method="euclidean", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
dist_dml <- as.matrix(dist_dml)
colnames(dist_dml) <- rownames(dist_dml) <- dm$Ethnicity
```


#### Correlation by Ethnicity
```{r fig.align = "center"}
jColFun <- colorRampPalette(brewer.pal(n = 9, "Blues"))

heatmap.2(dist_dml, col=rev(jColFun(256)), margin=c(8,15),
          Colv=TRUE, Rowv = TRUE, cexRow=1, cexCol=1,
          dendrogram ="both", trace="none", main="",
          hclustfun = function(x) hclust(x, method = "ward.D2"), 
          distfun = function(x) dist(x, method = "euclidean"),
          colsep=c(1:50), rowsep=c(1:50),
          sepcolor="#FFFFFF", sepwidth=c(0.0005,0.0005), 
          key="TRUE", keysize=1, density.info="none", symkey=0,
          key.title = NA, key.xlab = NA, key.ylab = NA,
          key.par=list(mgp=c(1.5, 0.5, 0), mar=c(2.5, 2.5, 1, 0)))
```
